### 2020-10-07 paper/natastron/paper.tex

\usepackage{chngcntr}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage[ ]{hyperref}
\graphicspath{{Images/}}
\usepackage[symbol]{footmisc}

@@

@@

\noindent Oliver J. Hall$^{1,2,3,}$\footnote[1]{Email: \texttt{oliver.hall@esa.int} | Twitter: \texttt{@asteronomer} | GitHub: \texttt{@ojhall94}}
	Guy R. Davies$^{2,3}$, 
	Jennifer van Saders$^{4,5,6}$,
	Martin B. Nielsen$^{2,3}$
	Mikkel N. Lund$^{3}$, 
	William J. Chaplin$^{2,3}$, 
	Rafael A. Garc\'ia$^{7, 8}$, 
	Louis Amard$^{9}$,
	Angela A. Breimann$^{9}$, 
	Saniya Khan$^{2,3}$, 
	Victor See$^{9}$, 
	Jamie Tayar$^{4, 10}$
	\\

@@

@@

\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise. Radial oscillations ($\ell = 0$), which are also visible, do not split. In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}. Further details on these data can be found in \textbf{Methods}.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{data.pdf}
	\caption{Our sample of 95 stars from the `Kages' and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}. The dashed lines indicate our classification boundaries: main sequence (circles, $\teff < 6250\, K$, $\logg < 4\, \rm{dex}$), potential sub-giants (squares, $\teff < 6250\, K$, $\logg > 4\, \rm{dex}$), and `hot' stars (triangles, $\teff > 6250\, K$). The Sun is shown with the `$\odot$' symbol, and has an age of $4.6\, \rm{Gyr}$ \cite{bonanno+frohlich2015}. The solid lines are evolutionary tracks generated using MESA \cite{paxton+2017}, for a metallicity of $Z = 0.01493$ and helium content of $Y = 0.26588$. Left to right, they represent masses of $1.5$, $1.25$, $1$ and $0.75\, M_\odot$. Vertical errorbars are too small to be visible \cite{hunter2007}.}
	\label{fig:sample}
\end{figure}

@@

We compared our results with both published and unpublished asteroseismic rotation rates \cite{davies+2016, lund+2017,davies+2015, nielsen+2015, benomar+2018}, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies. To some degree this was expected, as  for stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably. We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textbf{Methods}).\\

@@

Figure \ref{fig:protlit} shows a comparison between 48 stars from our sample for which spot  rotation rates had previously been measured. Rotation rates from spot modulation are subject to measuring multiples of the true rotation rate, and also sometimes over-correct for this effect. This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the figure. We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid outliers (transparent in the Figure). Our fit found a value of $m = 0.96 \pm 0.03$, showing a close agreement ($<2\sigma$) between asteroseismic and surface rotation rates on a population level. 
%Of the stars used in this comparison, 21 had a median value of $P_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  
This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{gizon+2013, chaplin+2013, nielsen+2015, benomar+2015}, and so we concluded that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{Images/surf-seis-comparison.pdf}
	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars. Literature values were taken, in order of priority, from: \cite{garcia+2014} and \cite{nielsen+2013} (i.e. if a value was reported in \cite{nielsen+2013} and also in \cite{garcia+2014}, the latter was used). Stars used in \cite{vansaders+2016} are highlighted. The four triangles represent stars included in the original \cite{nielsen+2015} work. The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines. The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure. Stars that were not included in the fitting process are transparent. The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
	\label{fig:protlit}
\end{figure}

\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}  The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation. The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}

Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic TRILEGAL populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{girardi+2012,vansaders+2019}. These synthetic populations were then altered to match the distribution of existing catalogues of stars in the \kepler field in order to replicate the \kepler selection effect \cite{berger+2020}, and evolved following a standard or WMB braking law. For the full details on how these models were constructed, see \textbf{Methods}.

In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, Excluding those with a number of effective samples $n_{\rm eff} < 25\%$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016} (see \textbf{Extended Data Table 1}). The remaining sample of 73 stars contained 4 potential sub-giants, 22 `hot' stars and 47 main sequence stars. Figure \ref{fig:fullsample} shows these stars plotted over the top of both the standard and WMB population models in rotation-temperature space, alongside the stars not used in the gyrochronology analysis (shown without uncertainties).

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{fullsample.png}
	\caption{Stars for which rotation was measured in this work, plotted over TREILGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution. The 21 Stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text). Circles, squares and triangles denote main sequence, sub-giant, and `hot' stars respectively. Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are shown in purple, to indicate that they fall outside the functional range of the \cite{vansaders+2019} stellar models. Note that only period-temperature space is shown here, but when evaluating between the two model prescriptions we also considered mass, age and metallicity. The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
	\label{fig:fullsample}
\end{figure*}

@@

\textbf{Results of comparing models:} We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $P_{\rm s}$ for that star. In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $P_{\rm{s}}$. This was done for the full ensemble of 73 stars, as well as for the three different stellar types. These joint probabilities can be seen in Figure \ref{fig:gyroresults} in the left-hand plot. The cumulative probability can be seen in the right-hand plot. In both of these plots, the left-hand side holds 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred. When only considering the 47 main sequence stars, for which we expect the effects of weakened magnetic braking to be strongest, this rises to 99.2\%.

Both hot and sub-giant stars do not strongly prefer one model over the other (both crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that the rotation rates of both these stellar types are not expected to be strongly influenced by weakened magnetic braking. When performing this analysis on the full ensemble of 91 stars for which seismic rotation was measured, this the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%. \\

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{modelresults.pdf}
	\caption{Posterior estimates of the mixture model parameter $P_{\rm s}$, broken down by stellar classification. A value of $P_{\rm s}$ close to zero indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 1 indicates that the data are more consistent with a standard rotational evolution scenario. \textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications. \textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types.}
	\label{fig:gyroresults}
\end{figure}

\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases. We found that the joint posterior distribution did not change significantly when excluding stars with a metallicity outside the model range (purple in Figure \ref{fig:fullsample}), or those with extremely small uncertainties on asteroseismic mass. Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.

@@

Weakened magnetic braking was first proposed by van Saders et al. (2016) \cite[hereafter the `van Saders' study]{vansaders+2016} in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages. This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{nielsen+2015, angus+2015, davies+2015}. The theory of weakened magnetic braking has been both reinforced by recent studies \cite{metcalfe+egeland2019}, as well as disputed \cite{lorenzo-oliveira+2019}, at least at the critical Rossby number originally proposed.

@@

All analysis performed as part of this work is stored in an online public repository\footnote{\url{https://github.com/ojhall94/malatium}}.\\

%\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\

\textbf{Acknowledgments}:The authors would like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions. 
OJH, GRD and WJC acknowledge the support of the UK Science and Technology Facilities Council (STFC). 
JvS acknowledges support from the TESS Guest Investigator Program (80NSSC18K18584).
MBN acknowledges support from the UK Space Agency
This work has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (CartographY GA. 804752)
Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106). 
LA, AB and VS acknowledge funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation program (grant agreement No. 682393 AWESoMeStars). AB also acknowledges the support of the College of Engineering, Mathematics and Physical Sciences at the University of Exeter.
RAG acknowledges the support from the PLATO and GOLF CNES grants.
JT acknowledges that support for this work was provided by NASA through the NASA Hubble Fellowship grant $\#51424$ awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
The computations described in this paper were performed using the University of Birmingham's BlueBEAR HPC service.
This paper includes data collected by the Kepler mission and obtained from the MAST data archive at the Space Telescope Science Institute (STScI). Funding for the Kepler mission is provided by the NASA Science Mission Directorate. STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5–26555.\\

% The best way to enter references is to use BibTeX:
%\bibliographystyle{naturemag}
%\bibliography{library.bib} %

@@

\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H.. (email: oliver.hall@esa.int).

\clearpage

\input{methods.tex}

\input{si.tex}

\input{ed.tex}

\bibliographystyle{naturemag}
\bibliography{library.bib} %

>>>>

\usepackage{chngcntr}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{lscape}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[ ]{hyperref}
\graphicspath{{Images/}}
%\usepackage[symbol]{footmisc}

@@

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

@@

\noindent Oliver J. Hall$^{1,2,3,}$\footnote[1]{Email: \texttt{oliver.hall@esa.int} | Twitter: \texttt{@asteronomer} | GitHub: \texttt{@ojhall94}},
	Guy R. Davies$^{2,3}$, 
	Jennifer van Saders$^{4,5,6}$,
	Martin B. Nielsen$^{2,3}$,
	Mikkel N. Lund$^{3}$, 
	William J. Chaplin$^{2,3}$, 
	Rafael A. Garc\'ia$^{7, 8}$, 
	Louis Amard$^{9}$,
	Angela A. Breimann$^{9}$, 
	Saniya Khan$^{2,3}$, 
	Victor See$^{9}$, 
	Jamie Tayar$^{4, 10}$
	\\

@@

\renewcommand*{\thefootnote}{\arabic{footnote}}
\setcounter{footnote}{0}

@@

\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode\footnote{\textit{Pressure} modes, the type of oscillation visible in main sequence stars.} oscillations for each star, of which the latter have significantly lower signal-to noise. Radial oscillations ($\ell = 0$), which are also visible, do not split. In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}. Further details on these data can be found in \textbf{Methods}.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.6\textwidth]{data.pdf}
	\caption{Our sample of 95 stars from the `Kages' and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}. The dashed lines indicate our classification boundaries: main sequence (circles, $\teff < 6250\, K$, $\logg < 4\, \rm{dex}$), potential sub-giants (squares, $\teff < 6250\, K$, $\logg > 4\, \rm{dex}$), and `hot' stars (triangles, $\teff > 6250\, K$). The Sun is shown with the `$\odot$' symbol, and has an age of $4.6\, \rm{Gyr}$ \cite{bonanno+frohlich2015}. The solid lines are evolutionary tracks generated using MESA \cite{paxton+2017}, for a metallicity of $Z = 0.01493$ and helium content of $Y = 0.26588$. Left to right, they represent masses of $1.5$, $1.25$, $1$ and $0.75\, M_\odot$. Vertical errorbars are too small to be visible \cite{hunter2007}.}
	\label{fig:sample}
\end{figure}

@@

We compared our results with both published and unpublished asteroseismic rotation rates \cite{nielsen+2015,davies+2015,davies+2016, lund+2017, benomar+2018}, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with multiple other studies. To some degree this was expected, as  for stars viewed near pole-on the split modes of oscillation have extremely low power, making them hard to detect reliably. We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we considered our asteroseismic rotation measurements to be robust (for a full justification, see \textbf{Methods}).\\

@@

Figure \ref{fig:protlit} shows a comparison between 48 stars from our sample for which spot  rotation rates had previously been measured. Rotation rates from spot modulation are subject to measuring multiples of the true rotation rate, and also sometimes over-correct for this effect. This is not the case for asteroseismic rotation, and so some stars may appear at the 2:1 and 1:2 lines in the figure. We fit a line of the form $P_{\rm surf} = m \times P_{\rm seis}$, using the larger of the asymmetrical uncertainties on asteroseismic rotation, and excluding stars above the 1.8:1 line to avoid outliers (transparent in the Figure). Our fit found a value of $m = 0.96 \pm 0.03$, showing a close agreement ($<2\sigma$) between asteroseismic and surface rotation rates on a population level. 
%Of the stars used in this comparison, 21 had a median value of $P_{\rm s}$ in the gyrochronology analysis. We repeated the model fit for these stars only, and found a value of $m = 0.96 \pm 0.04$.  
This overall agreement between spot and seismic rotation rates is in line with previous studies of Sun-like stars \cite{nielsen+2015, benomar+2015, gizon+2013, chaplin+2013}, and so we concluded that our asteroseismic ensemble can be reliably used to draw inferences about gyrochronology.\\

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.6\textwidth]{Images/surf-seis-comparison_update.pdf}
	\caption{Comparisons between asteroseismic and photometric measures of stellar rotation, for 48 stars. Literature values were taken, in order of priority, from: Garcia et al. (2014) \cite{garcia+2014} and Nielsen et al. (2013) \cite{nielsen+2013} (i.e. if a value was reported in Nielsen et al. (2013) and also in Garcia et al. (2014), the latter was used). Stars used in the original van Saders et al. (2019) \cite{vansaders+2016} study that first proposed weakened magnetic braking are highlighted. The four triangles represent stars included in the Nielsen et al. (2015) study \cite{nielsen+2015} that previously measured this relationship. The solid line indicates 1:1 line, while the dash-dotted lines represent 2:1 and 1:2 lines. The shaded region around the 1:1 line is the $1\sigma$ credible interval of the fit to the data, the result of which is shown as the title of the figure. Stars that were not included in the fitting process are transparent. The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
	\label{fig:protlit}
\end{figure}

\textbf{Comparing gyrochronology models:} To evaluate the implications of our seismic ensemble for gyrochronology, we compared our new asteroseismic rotation rates to two population models of rotational evolution \cite{vansaders+2019}: a `standard' model, which assumes a traditional angular momentum transport through magnetically driven stellar winds \cite{skumanich1972, kawaler1988}, and one where weakened magnetic braking takes place (hereafter the `WMB model') \cite{vansaders+2016}  The WMB model was identical to the standard model in its input physics, except for the condition that angular momentum loss ceases above a critical Rossby number of $Ro_{\rm crit} = 1.97$\footnote{The Rossby number may be defined as $Ro \equiv P/\tau_{\rm cz}$, where $\tau_{\rm cz}$ is the convective turnover timescale, and $P$ is the rotation. The Rossby number roughly scales inversely with stellar activity (and so increases as stars age).}.

Instead of comparing our rotation rates directly to models of individual stars, we instead compared them to synthetic TRILEGAL populations based on what the \textit{Kepler} field would look like under these two different braking laws \cite{vansaders+2019, girardi+2012}. These synthetic populations were then altered to match the distribution of existing catalogues of stars in the \kepler field in order to replicate the \kepler selection effect \cite{berger+2020}, and evolved following a standard or WMB braking law. For the full details on how these models were constructed, see \textbf{Methods}.

In order to ensure our results were based on the most robust rotation measurements, we focused on the stars with the best convergence metrics in the mode frequency fitting, excluding those with a number of effective samples $n_{\rm eff} < 1000$ and a Gelman-Rubin metric of $\hat{R}>1.1$ \cite{gelman+rubin1992,salvatier+2016} (see \textbf{Extended Data} Table \ref{tab:results}). Two stars with low metallicities ($< -0.8\, \rm {dex}$) that fell outside the boundaries of our stellar models were also excluded. The remaining sample of 73 stars contained 4 potential sub-giants, 22 `hot' stars and 47 main sequence stars. Figure \ref{fig:fullsample} shows these stars plotted over the top of both the standard and WMB population models in rotation-temperature space, alongside the stars not used in the gyrochronology analysis (shown without uncertainties).

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{fullsample.png}
	\caption{Stars for which rotation was measured in this work, plotted over TRILEGAL \cite{girardi+2012} stellar population models evolved under standard (top) and weakened magnetic braking (WMB, bottom) prescriptions of angular momentum evolution. The 21 Stars that were excluded from the gyrochronology analysis are marked with crosses and without uncertainties (see text). Circles, squares and triangles denote main sequence, sub-giant, and `hot' stars respectively. Stars with a metallicity of $\bigl\lvert \feh \bigl\rvert > 0.4$ are shown in purple, to indicate that they fall outside the functional range of the stellar models  \cite{vansaders+2019}. Note that only period-temperature space is shown here, but when evaluating between the two model prescriptions we also considered mass, age and metallicity. The errorbars on the asteroseismic rotation represent the $15.9^{\rm th}$ and $84.1^{\rm st}$ percentiles on the measured posterior distributions.}
	\label{fig:fullsample}
\end{figure*}

@@

\textbf{Results of comparing models:} We fit our mixture model to each star individually, which yielded a posterior probability density for the value of $P_{\rm s}$ for that star. In order to assess the posterior probability for the full sample, we multiplied the individual posterior probabilities for $P_{\rm{s}}$. This was done for the full ensemble of 73 stars together, as well as for the three different stellar types separately. These joint probabilities can be seen in Figure \ref{fig:gyroresults} in the left-hand plot. The cumulative probabilities can be seen in the right-hand plot. In both of these plots, the left-hand side holds 98.4\% of the probability, indicating that the weakened magnetic braking model is preferred. When only considering the 47 main sequence stars, for which we expect the effects of weakened magnetic braking to be strongest, this rises to 99.2\%.

Both hot and sub-giant stars do not strongly prefer one model over the other (both crossing the $P_{\rm{s}} = 0.5$ line at roughly $45\%$), which is expected given that the rotation rates of both these stellar types are not expected to be strongly influenced by weakened magnetic braking. When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), this the total probability below $P_{\rm{s}} = 0.5$ is 96.6\%. \\

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{modelresults.pdf}
	\caption{Posterior estimates of the mixture model parameter $P_{\rm s}$, broken down by stellar classification. A value of $P_{\rm s}$ close to zero indicates that the data are more consistent with a rotational evolution that includes weakened magnetic braking, whereas a value close to 1 indicates that the data are more consistent with a standard rotational evolution scenario. \textit{Left:} the product of histograms of the posterior estimates for 73 stars, or subsets thereof for different stellar classifications. \textit{Right:} the cumulative posterior probability for 73 stars, or subsets thereof for different stellar types. On the y-axis of the left hand plot, $p(P_{\rm s} | \mathcal{D})$ represents the posterior distribution on $P_{\rm s}$ given the data. The product symbol represents the sum of the posteriors for individual stars $i$, for a total of $N$ stars (which differs depending on the stellar type being shown).}
	\label{fig:gyroresults}
\end{figure}

\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases. We found that the joint posterior distribution did not change significantly when excluding stars with a metallicities that fell only slightly outside the model range, or those with extremely small uncertainties on asteroseismic mass (see \textbf{Methods}). Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.

@@

Weakened magnetic braking was first proposed by van Saders et al. (2016) \cite[hereafter the `van Saders' study]{vansaders+2016} in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages. This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{angus+2015, nielsen+2015,  davies+2015}. The theory of weakened magnetic braking has been both reinforced by recent studies \cite{metcalfe+egeland2019}, as well as disputed \cite{lorenzo-oliveira+2019}, at least at the critical Rossby number originally proposed.

@@

\input{bblpaper.tex}

\newpage
\textbf{Acknowledgments}:The authors would like to thank Sean Matt, Ellis Avallone, Alex Dixon, Warrick Ball and Brett Morris for helpful discussions. 
OJH, GRD and WJC acknowledge the support of the UK Science and Technology Facilities Council (STFC). 
JvS acknowledges support from the TESS Guest Investigator Program (80NSSC18K18584).
MBN acknowledges support from the UK Space Agency
This work has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (CartographY GA. 804752)
Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106). 
LA, AB and VS acknowledge funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation program (grant agreement No. 682393 AWESoMeStars). AB also acknowledges the support of the College of Engineering, Mathematics and Physical Sciences at the University of Exeter.
RAG acknowledges the support from the PLATO and GOLF CNES grants.
JT acknowledges that support for this work was provided by NASA through the NASA Hubble Fellowship grant $\#51424$ awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
The computations described in this paper were performed using the University of Birmingham's BlueBEAR HPC service.
This paper includes data collected by the Kepler mission and obtained from the MAST data archive at the Space Telescope Science Institute (STScI). Funding for the Kepler mission is provided by the NASA Science Mission Directorate. STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5–26555.\\

@@

\textbf{Correspondence:} Correspondence and requests for materials should be addressed to O.J.H.. (email: oliver.hall@esa.int).\\

\clearpage
\input{methods.tex}

\clearpage
\input{ed.tex}
